On Secure Delegation of SampBQP with a Classical Client

### 2019-12-23 qpip.tex
Make editorial changes to hybrid client protocol

\subsection{TODO 1 qubit}

\Ethan{Fix title}

@@

\begin{observation}
	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{observation}
\begin{proof}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{proof}

\begin{theorem}
	Let $L\in\SampBQP$. Then there exists some $\QPIP_1$ protocol for $L$ with completeness negligible to perfect and soundness $(O(T^{-c}), 1-O(T^{-c}))$ for any constant $c$. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{theorem}
\begin{proof}
	Set the following variables
	\begin{itemize}
		\item $\varepsilon=T^{-c}$
		\item $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\item $n$ large enough so by Chernoff bound:
			\begin{itemize}
				\item[$\circ$] $q'=P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
			\end{itemize}
		\item $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
	\end{itemize}

	We claim that the following protocol does what is required:
	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{Our $\QPIP_{XZ}$ protocol}
		\label{AlgAmp1}
		\begin{algorithmic}[1]
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $n+m$ copies; $m$ for output and $n$ for checking
			\State $c\gets0$
			\For{$i\gets1, N$}
			    \If{Register is for checking}
			    \State The verifier runs \autoref{AlgGroundStateCheck} on the register
			    \If{Test passes}
			        $c\gets c+1$
			    \EndIf
			    \ElsIf{Register is for outputting}
			    \State The verifier measures the clock register
			    \If{measurement result $\geq\frac{T}{2}$}
			        \If{$y$ isn't set}
			            $y\gets$ Measure the data register
                    \EndIf
			    \EndIf
			    \Else
			    \State Measure the entire register in standard basis
			    \EndIf
			\EndFor
			\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
			\If{$y$ is set}
			\State output $y$
			\Else
			\State Reject
			\EndIf
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

	This clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted. Let $\sigma$ be the state the prover sends.

	Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers. Denote the state after the random permutation as

@@

	Let $\tilde{\Pi}$ be some fixed permutation. Then it is easy to check that

	$$\tilde{\Pi}\sigma'\tilde{\Pi}^\dagger=\sigma'$$

	So $\sigma'$ is permutation-invariant and we can apply \autoref{deFinetti}:

	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+n}(\sigma'-\sum_i w_i\rho_i^{\otimes n+m})}=O(\varepsilon)$$

	Note that $\tilde\sigma=\sum_i w_i\rho_i^{\otimes n+m}$ is a classical probability distribution over inputs $\rho_i^{\otimes n+m}$ with $w_i$ as weights.

	Let $p_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}.
	So the accept chance of this prover is $\sum_j w_j p_j>\delta$
	By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i p_i}{\sum_j w_j p_j}$.

	Let
	$$J=\set{j:q_j\leq q'}$$

	Then the following is clearly negligible:
	$$\sum_{j\in J} w_j q_j$$

	And so is
	$$\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}$$

@@

	Such $\rho_i$ are $O(\poly(\varepsilon))$-close to $\ket{\psi_{C(x)}}$.

	So we simply measure the time register until we get measurement result $t\geq T$. The probability of failing to do so after all $m$ copies is $\frac{1}{2^m}$ which is negligible.

@@

\subsection{TODO 0 qubits}

\Ethan{Fix title}

>>>>

\subsection{Protocol for Hybrid Client}

@@

\begin{observation}
	\label{ProtoGroundStateCheck}
	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{observation}
\begin{proof}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{proof}

\begin{theorem}
	Let $L\in\SampBQP$. Then there exists some $\QPIP_1$ protocol for $L$ with completeness negligible to perfect and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{theorem}
\begin{proof}
	Set the following variables
	\begin{itemize}
		\item $\varepsilon=T^{-c}$
		\item $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\item $n$ large enough so the following quantities are negligible in $\varepsilon$ by the Chernoff bound:
			\begin{itemize}
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$
			\end{itemize}
		\item $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
	\end{itemize}

	With these parameters, we claim that \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} does what is required.
	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{Our $\QPIP_1$ protocol}
		\label{ProtoQPIP1}
		\begin{algorithmic}[1]
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
			\State $c\gets0$
			\State $y\gets$null
			\For{$i\gets1, N$}
			    \If{Copy is for checking}
				\State The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
			    \If{Test passes}
			        $c\gets c+1$
			    \EndIf
			    \ElsIf{Copy is for outputting}
			    \State The verifier measures the copy in standard basis
			    \If{measurement result of the clock register $\geq\frac{T}{2}$}
			        \If{$y=$null}
			            $y\gets$ measurement result of the data register
                    \EndIf
			    \EndIf
			    \Else
			    \State The verifier measures the entire register in standard basis
			    \EndIf
			\EndFor
			\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
			\If{$y\ne$null}
			\State output $y$
			\Else
			\State Reject
			\EndIf
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

	It clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted. Let $\sigma$ be the state the prover sends to the verifier.

	Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers.
	A random permutation is equivalent to a classical mix over all possible permutations of $\sigma$:

@@

	Now we verify that $\sigma'$ is permutation-invariant.
	Let $\tilde{\Pi}$ be some fixed permutation, then clearly:
	$$\tilde{\Pi}\sigma'\tilde{\Pi}^\dagger=\sigma'$$

	So we can apply \autoref{deFinetti}. $\exists\set{w_i, \rho_i}$ such that:
	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+n}(\sigma'-\sum_i w_i\rho_i^{\otimes n+m})}=O(\varepsilon)$$

	Note that $\tilde\sigma=\sum_i w_i\rho_i^{\otimes n+m}$ is a classical mix over $\rho_i^{\otimes n+m}$ with weights $w_i$.

	Let $p_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}.
	So the accept chance of this prover is $\sum_j w_j p_j>\delta$
	By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otimes n+m}$ is then $\frac{w_i p_i}{\sum_j w_j p_j}$.

	Let
	$$J=\set{j:q_j\leq P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]}$$

	Recall that then each $q_j$ must be negligible by how we picked $n$. Hence the following is clearly negligible:
	$$\sum_{j\in J} w_j q_j$$

	And so is
	$$\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}=\frac{\sum_{j\in J} w_j q_j}{\delta}$$

@@

	Such $\rho_i$ are $O(\negl(\varepsilon))$-close to $\ket{\psi_{C(x)}}$, by applying a Chernoff bound to \autoref{ThmXZCheck}.

	The probability of measuring $t\geq T$ on the clock register of $\ket{\psi_{C(x)}}$ is $\frac{1}{2}$, so the probability of failing to do so after $m$ attempts is negligible.

@@

\subsection{Protocol for Fully Classical Client}

\Ethan{TODO read Mahadev's?}
